FTLR proof cases

### 2018-06-22 fully-abstract-comp/ftlr-proof-cases.tex
Remove obsolete TODOs.
compilation issue
Fix a cross-cutting problem related to a bad definition of linking.
The problem was that linking of components was poorly designed, with components
already expected to already include the exports of the components they link
with, rather than them being inserted by the linking process.
This worked in principle, except that a single component could not be linked
with two different other components (as in the statement of full abstraction).
The fix is to introduce a more reasonable linking setup: components specify
imports as symbol-address pairs indicatin

    We know that the two register-files are related which in particular means that
    the values in register $\rstk$ are related. Now consider the following cases:
    \lau{TODO: Perhaps make a lemma that says if source fail and target step to
      fail, then the two configurations are in $\lro$.}
    \item $\Phi_S(\rstk) \neq \stkptr{\_,\_,\_,\_}$\\

@@

  Take an $r \neq \pcreg$ and $\gc = (\ta,\stkb,\gsigrets,\gsigcloss)$.
  By Lemma~\ref{lem:untrusted-source-values-are-reasonable}, it suffices to prove the following:
  \begin{itemize}
  \item $\npair{(w,\_)} \in \lrv(W_w)$: follows from $\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_R)$.
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$: by assumption.
  \item $\purePart{W_w} \oplus \purePart{W_M}$ is defined: By Lemma~\ref{lem:purePart-oplus}
  \item $\pwheap[W_w](r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$: TODO
  \item $\dom(\code) \subseteq \ta$: Follows from $\trust = \trusted$ by the choice of $\trust$.
  \item $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$: TODO
  \end{itemize}

>>>>

    We know that the two register-files are related which in particular means that
    the values in register $\rstk$ are related. Now consider the following cases:
    \lau{TODO: Perhaps make a lemma that says if source fail and target step to
      fail, then the two configurations are in $\lro$.}
    \begin{itemize}
    \item $\Phi_S(\rstk) \neq \stkptr{\_,\_,\_,\_}$

@@

  Take an $r \neq \pcreg$ and $\gc = (\ta,\stkb,\gsigrets,\gsigcloss)$.
  By Lemma~\ref{lem:untrusted-source-values-are-reasonable}, it suffices to prove the following:
  \begin{itemize}
  \item $\npair{(w,\_)} \in \lrv(W_w)$: follows from $\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_R)$.
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$: by assumption.
  \item $\purePart{W_w} \oplus \purePart{W_M}$ is defined: By Lemma~\ref{lem:purePart-oplus}
  \end{itemize}
